Social Attention for Autonomous Decision-Making in Dense Traffic

### 2019-09-09 main.tex
Update

\begin{abstract}
  TODO
\end{abstract}

@@

\begin{figure}[tp]
	\centering
	\includegraphics[width=0.25\textwidth]{img/coordinates}
	\includegraphics[width=0.25\textwidth]{img/map}
	\caption{The coordinates (left) and spatial-grid (right) representations}
\end{figure}

For instance, this representation is used in \citep{Bai2015, Gindele2015, Song2016, Sunberg2017, Paxton2017, Galceran2017, Chen2017}.

@@

\begin{table}[tp]
	\centering
	\begin{threeparttable}
		\caption{Characteristics of the agents}
		\label{tab:agents}
		\begin{tabular}{lccc}
			\toprule
			Architecture & \MLPC & \MLPG & \EgoAtt \\
			\midrule 
			Input sizes & [15, 7] & [?, ?, 7] & [1-15, 7] \\
			Layers sizes & [128, 128] &  [64, 64] & Encoder: [64, 64] \\
			& & & Attention $d_k$: 64\\
			& & & Decoder: [64, 64]\\
			Number of parameters & 3.0e4 & ? & 3.4e4 \\
			Permutation invariant & No & Yes & Yes \\
			\bottomrule
		\end{tabular}
	\end{threeparttable}
\end{table}

@@

TODO: figure

@@

By switching the priority road, the resulting policy changes: In the exact same initial state, the ego-vehicle takes way to incoming vehicles when its policy was trained on a priority road, and gives way otherwise. The only change between these two situations is the rules of interactions imposed on simulated vehicles, which showcases the ability of our proposed architecture to discover and exploit such interaction patterns.

@@

\section*{References}

>>>>

\begin{abstract}
  This work addresses the design of learning architectures in the context of high-level decision making for autonomous driving in a dense traffic setting. We focus on three challenges: dealing with a varying number of nearby vehicles, being invariant to the ordering chosen to describe the scene, and accounting for the existing interactions between the traffic participants.
\end{abstract}

@@

\begin{figure}[tp]
	\centering
	\includegraphics[width=0.25\textwidth]{img/coordinates}
	\includegraphics[width=0.25\textwidth]{img/map}
	\caption{The coordinates (left) and spatial-grid (right) representations}
	\label{fig:representation}
\end{figure}

This representation is illustrated in \autoref{fig:representation} and was used e.g. in \citep{Bai2015, Gindele2015, Song2016, Sunberg2017, Paxton2017, Galceran2017, Chen2017}.

@@

\begin{table}[tp]
	\centering
	\begin{threeparttable}
		\caption{Characteristics of the agents}
		\label{tab:agents}
		\begin{tabular}{lccc}
			\toprule
			Architecture & \MLPC & \MLPG & \EgoAtt \\
			\midrule 
			Input sizes & [15, 7] & [?, ?, 7] & [1-15, 7] \\
			Layers sizes & [128, 128] &  [64, 64] & Encoder: [64, 64] \\
			& & & Attention: $d_k=64$\\
			& & & Decoder: [64, 64]\\
			Number of parameters & 3.0e4 & ? & 3.4e4 \\
			Variable input size & No & No & Yes \\
			Permutation invariant & No & Yes & Yes \\
			\bottomrule
		\end{tabular}
	\end{threeparttable}
\end{table}

@@

This model is also more interpretable, as we can visualize the learnt attention matrix.

TODO: figure yield vs take way

@@

change the priority -> influences the rules of interactions -> changes the learnt behaviour.
By switching the priority road, the resulting policy changes: In the exact same initial state, the ego-vehicle takes way to incoming vehicles when its policy was trained on a priority road, and gives way otherwise. The only change between these two situations is the rules of interactions imposed on simulated vehicles, which showcases the ability of our proposed architecture to discover and exploit such interaction patterns.

@@
